Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: remove link between tuning and FS

% Wrapper approach
\noindent Wrappers \cite{chandrashekar2014, kohavi1997} apply algorithms that are also used for hyperparameter optimization such as 'Random Search' or 'Generic Simulated Annealing'.
First a (random) subset of features is chosen based on the selected algorithm.
In comparison to filters, no ranking is done in this step.
Now the model is fitted on the data and the performance is evaluated.
This is done multiple times, depending on the defined stopping criteria set by the user (performance, runtime, evaluations).
A disadvantage of this approach is that hyperparameter tuning can only be applied after the feature selection optimization finished.
Hence, the 'wrapper approach' is an expensive optimization method because two stages need to be run in sequential order.
Due to their extensive runtimes, wrappers were not considered in this work.

>>>>

% Wrapper approach
\noindent Wrappers \cite{chandrashekar2014, kohavi1997} apply search algorithms such as 'random search' or 'generic simulated annealing'.
First a (random) subset of features is chosen based on the selected algorithm.
In comparison to filters, no ranking is done in this step.
Now the model is fitted on the data and the performance is evaluated.
This is done multiple times, depending on the defined stopping criteria set by the user (performance, runtime, evaluations).
A disadvantage of this approach is that hyperparameter tuning can only be applied after the feature selection optimization finished.
Hence, the 'wrapper approach' is an expensive optimization method because two stages need to be run in sequential order.
Due to their extensive runtimes, wrappers were not considered in this work.
